Draft -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- Draft

### 2024-09-27 docs/_tex/index.tex
add results

Amoung the high altitude flights, the one acquired over the inner part
of Ria de Aveiro coastal lagoon covered the largest area with
approximately 1.5 km² (Figure~\ref{fig-Boat}). This site was dominated
by seagrass and red macroalgae. The classification provided consistent
results, with a patchy seagrass meadow mixed with red macroalgae on the
eastern part of the site. As shown in the zoom (Figure~\ref{fig-Boat}),
the edges of the meadow were mixed with green macroalgae (\emph{Ulva
sp.}), which the model agreed with (F1 score of 0.89 for green algae,
0.97 for seagrass and 0.98 for red algae).

@@

Figure~\ref{fig-pixelsize} shows an effect of the pixel size on the
agreement between the two products. The highest resolution in which the
resampling has been performed is 10 cm. At this resolution, the
agreement has already decreased from 78\% (red algae) to 94\%
(seagrass), depending on the class. As pixel size increases, the
agreement between the products declines steadily for all classes. This
decline is most pronounced for green algae, which experiences the
sharpest drop in agreement as pixel size increases beyond 10 m, reaching
below 0\% at a pixel size of 30 m. Seagrass maintain higher levels of
agreement at coarser resolutions, although a clear decline is still
observed, with seagrasses dropping from over 94\% at 10 cm to around
88\% at 30 m. Brown algae and red algae show a more moderate decline
compared to red algae, with agreement levels remaining around 62\% and
40\%, respectively, at 30 m resolution.

>>>>

Among the high altitude flights, the one acquired over the inner part of
Ria de Aveiro coastal lagoon covered the largest area with approximately
1.5 km² (Figure~\ref{fig-Boat}). This site was dominated by seagrass and
red macroalgae. The classification provided consistent results, with a
patchy seagrass meadow mixed with red macroalgae on the eastern part of
the site. As shown in the zoom (Figure~\ref{fig-Boat}), the edges of the
meadow were mixed with green macroalgae (\emph{Ulva sp.}), which the
model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass
and 0.98 for red algae).

@@

Figure~\ref{fig-pixelsize} demonstrated the effect of pixel size on the
agreement between two products. The highest resolution at which
resampling was performed was 10 cm. At this resolution, agreement rates
had already decreased, ranging from 78\% for red algae to 94\% for
seagrass, depending on the class. As pixel size increased, the agreement
between the products steadily declined across all classes. This decline
was most pronounced for green algae, which experienced the sharpest drop
in agreement as pixel size surpassed 10 m, falling below 0\% at a 30 m
pixel size. Seagrass maintained higher agreement levels at coarser
resolutions, though a clear decline was still observed, dropping from
over 94\% at 10 cm to around 88\% at 30 m. Brown algae and red algae
showed a more moderate decline in comparison, with agreement levels at
30 m resolution settling around 62\% and 40\%, respectively.

### 2024-09-27 index.qmd
add results

Amoung the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat). This site was dominated by seagrass and red macroalgae. The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site. As shown in the zoom (@fig-Boat), the edges of the meadow were mixed with green macroalgae (*Ulva sp.*), which the model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass and 0.98 for red algae).

@@

@fig-pixelsize shows an effect of the pixel size on the agreement between the two products. The highest resolution in which the resampling has been performed is 10 cm. At this resolution, the agreement has already decreased from 78% (red algae) to 94% (seagrass), depending on the class. As pixel size increases, the agreement between the products declines steadily for all classes. This decline is most pronounced for green algae, which experiences the sharpest drop in agreement as pixel size increases beyond 10 m, reaching below 0% at a pixel size of 30 m. Seagrass maintain higher levels of agreement at coarser resolutions, although a clear decline is still observed, with seagrasses dropping from over 94% at 10 cm to around 88% at 30 m. Brown algae and red algae show a more moderate decline compared to red algae, with agreement levels remaining around 62% and 40%, respectively, at 30 m resolution.

>>>>

Among the high altitude flights, the one acquired over the inner part of Ria de Aveiro coastal lagoon covered the largest area with approximately 1.5 km² (@fig-Boat). This site was dominated by seagrass and red macroalgae. The classification provided consistent results, with a patchy seagrass meadow mixed with red macroalgae on the eastern part of the site. As shown in the zoom (@fig-Boat), the edges of the meadow were mixed with green macroalgae (*Ulva sp.*), which the model agreed with (F1 score of 0.89 for green algae, 0.97 for seagrass and 0.98 for red algae).

@@

@fig-pixelsize demonstrated the effect of pixel size on the agreement between two products. The highest resolution at which resampling was performed was 10 cm. At this resolution, agreement rates had already decreased, ranging from 78% for red algae to 94% for seagrass, depending on the class. As pixel size increased, the agreement between the products steadily declined across all classes. This decline was most pronounced for green algae, which experienced the sharpest drop in agreement as pixel size surpassed 10 m, falling below 0% at a 30 m pixel size. Seagrass maintained higher agreement levels at coarser resolutions, though a clear decline was still observed, dropping from over 94% at 10 cm to around 88% at 30 m. Brown algae and red algae showed a more moderate decline in comparison, with agreement levels at 30 m resolution settling around 62% and 40%, respectively.
